A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-10-21 linear.tex
tiny correction in entropy def

{\bf note: important to use largrangian pressure pert}
In Table \ref{si_compare} we also calculate the phase difference
between the Lagragian pressure perturbation and density perturbations
as    
\begin{align*} 
\varphi = -\sgn(\omega)\arg\left(\Delta P\Delta\rho^*\right), 
\end{align*}
so that $\varphi > 0 $ indicates pressure lagging behind density, which
is true for all the cases. In particular, `linB' indicates that growth
rates vanish as $\varphi \to 0$.  
Thus the streaming instability stems  
from the gas pressure evolution lagging behind that of the total
density (and hence behind the dust density for isothermal gas).

>>>>

{\bf note: important to use largrangian pressure pert}
In Table \ref{si_compare} we also calculate the phase difference
between the Lagragian pressure perturbation and density perturbations
as    
\begin{align*} 
\varphi &= -\sgn(\omega)\arg\left(\Delta P\Delta\rho^*\right)
 &       = -\sgn(\omega)\arg\left(\Delta\rhog\Delta\rhod^*\right),\notag
\end{align*}
where we have applied the isothermal equation of state for the second equality.
Then $\varphi > 0 $ indicates pressure lagging behind density, which
is true for all the cases. In particular, `linB' indicates that growth
rates vanish as $\varphi \to 0$.  
Thus the streaming instability stems  
from the gas pressure evolution lagging behind that of the dust 
density.
